\textit{Supplementary materials for}: Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-01-17 paper/supplement.tex
- finished "random conditions" description - added bryan as a co-author (yay!) - working on description of order manipulation conditions
draft of order manipulation conditions:   - added Allison as an author (yay!)   - added "stick" figure to illustrate stochastic word ordering procedure   - added descriptions + equations for order manipulation conditions
- working on results section - added Campbell as an author (yay!)
quick round of edits through end of methods
backing up progress on discussion section   - added a more detailed summary and overview of the key results
inputting a round of wri

\title{\textit{Supplementary materials for}: Carryover effects in free recall reveal how prior experiences influence memories of new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Kirsten Ziman\textsuperscript{1, 2}, Emily Whitaker\textsuperscript{1},\\Paxton C. Fitzpatrick\textsuperscript{1}, Madeline R. Lee\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1, 3}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Princeton University\\\textsuperscript{3}Akili Interactive\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

    \caption{\textbf{Recall accuracy by study list number.}  Each panel displays the average recall accuracy (across participants) as a function of the number of studied lists for the
    random (control) conditions (\textbf{A.}), order manipulation conditions (\textbf{B.}), and adaptive conditions (\textbf{C.}.  The conditions are denoted by color.  Note that the first four
    lists in all of the ``adaptive'' conditions were ordered randomly to compute a baseline fingerprint for each participant prior to initiating the adaptive ordering procedure.  All error
    ribbons denote bootstrap-estimated 95\% confidence intervals, calculated across participants.}
        \label{fig:accuracy-by-list}
\end{figure}

>>>>

\title{\textit{Supplementary materials for}: Feature and order manipulations in
a free recall task affect memory for current and future lists}

\author{Jeremy R. Manning\textsuperscript{1, *}, Kirsten
Ziman\textsuperscript{1, 2}, Emily Whitaker\textsuperscript{1},\\Paxton C. 
Fitzpatrick\textsuperscript{1}, Madeline R. Lee\textsuperscript{1}, Allison M
Frantz\textsuperscript{1},\\Bryan J. Bollinger\textsuperscript{1}, Campbell E.
Field\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1,
3}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Princeton
University\\\textsuperscript{3}Akili
Interactive\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

@@

    \caption{\textbf{Recall accuracy by study list number.}  Each panel displays the average recall accuracy (across participants) as a function of the number of studied lists for the
    random conditions (\textbf{A.}), order manipulation conditions (\textbf{B.}), and adaptive conditions (\textbf{C.}.  The conditions are denoted by color.  Note that the first four
    lists in all of the ``adaptive'' conditions were ordered randomly to compute a baseline fingerprint for each participant prior to initiating the adaptive ordering procedure.  All error
    ribbons denote bootstrap-estimated 95\% confidence intervals, calculated across participants.}
        \label{fig:accuracy-by-list}
\end{figure}
